Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2023-01-11 edubots_surveys.Rnw
Went for institutional

The introduction of chatbots and chatbot technology will be helped by the fact
that no discernible differences are found in the survey between different
demographic groups. Even though chatbots do have some potential for
personalization or customization based on the class material, student, and
teaching staff, the general introduction of the technology can be done in a
general way and for all disciplines, types or degrees, teaching experience, and
gender.

>>>>

The introduction of chatbots and chatbot technology will be helped by the fact
that no discernible differences are found in the survey between different
demographic groups. Even though chatbots do have some potential for
personalization or customization based on the class material, student, and
teaching staff, the institutional introduction of the technology can be done in a
general way and for all disciplines, types or degrees, teaching experience, and
gender.
